---
title: "ARIMA Model in R"
output:
  html_document:
    df_print: paged
---

by Kunaal Naik 
YouTube - [www.youtube.com/fxexcel](http://www.youtube.com/fxexcel) 
GitHub Link - [Download Code and Dataset](https://github.com/FunXExcel/YouTube-Working-Files/tree/master/Time%20Series%20Forecasting/ARIMA%20model%20in%20R)

*Links open in another window*


#### 1/ Import Libraries
```{r echo=TRUE, message=FALSE}
library(forecast)
library(tseries)
```

#### 2/ Change working Directory
Provide the path in which you data is present
```{r}
setwd("C:\\Users\\DELL\\Documents\\__Fun_X_Excel_Channel_Videos\\Arima\\R")
```

#### 3/ Import Sales Dataset
```{r}
sales <- read.csv("sales.csv")
```

#### 4/ Convert sales_k column to Time Series object
```{r}
sales_ts <- ts(sales$Sales_k,start=c(1972),frequency=12)
```

#### 5/ Plot Sales Time series using autoplot (forecast library)
```{r}
autoplot(sales_ts)
```

#### 6/ Check Stationarity
Stationarity : A stationary process has a mean and variance that do not change overtime and the process does not have trend.

##### Perform ADF Test
Null Hypothesis - Non Stationary (Do **NOT** Reject if P value > sig lvl {1%, 5%, 10%} )
```{r}
adf.test(sales_ts)
```
Since P is not greater sig lvl - The Series is **NON Stationary**

We will take the first difference to make it Stationary

##### Perform ADF Test on First Difference
```{r}
sales_ts_d1 <- diff(sales_ts, differences = 1)
adf.test(sales_ts_d1)
```
```{r}
autoplot(sales_ts_d1)
```

Much better and Stationary. 

##### ARIMA (p,d,q)
q term will remain 1 - since we took the first difference 

#### 7/ Run ACF test to select AR term or the p term
ACF - Correlation between lags
```{r}
Acf(sales_ts)
```
##### We will run the same test with differenced series
```{r}
Acf(sales_ts_d1)
```

#### 8/ Run PACF test to select MA term or the q term 
PACF - Correlation between moving averages
```{r}
Pacf(sales_ts)
```
##### We will run the same test with differenced series
```{r}
Pacf(sales_ts_d1) 
```

#### 9/ BASIC ARIMA
We will use p and q as 6; d will be 1
```{r}
tsMod <- Arima(y = sales_ts,order = c(6,1,6))
```

#### 10/ Summary of the model
```{r}
tsMod
```

#### 11/ Forecast 12 periods ahead
```{r}
forecast(tsMod,h=12)
```

#### 12/ Plot Sales with forecast 
```{r}
autoplot(forecast(tsMod,h=12))
```

#### 13/ LJung test for serial correlation on Residuals 
- Null Hypothesis : No Serial correlation up to a certain lag
- Reject NUll Hypothesis if p-value less than significant level(0.05)
```{r}
Box.test(tsMod$residuals, type = 'Ljung-Box')
```
